A Partitioning Algorithm for Maximum Common Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-14 paper/paper.tex
Fixed a couple of errors

\paragraph{Vertex labels, edge labels, directed}
Cumulative run times for this class of instances are in \cref{figre:33ved-cumulative}.
Again, \McClique\ is over an order of magnitude faster than the best CP algorithm,
which is CP-MAC in this case.  The clique encoding, however, outperforms the other
algorithms on these labelled instances, except in the easy region at the left
of the graph.

>>>>

\paragraph{Vertex labels, edge labels, directed}
Cumulative run times for this class of instances are in \cref{figure:33ved-cumulative}.
Again, \McSplit\ is over an order of magnitude faster than the best CP algorithm,
which is CP-MAC in this case.  The clique encoding, however, outperforms the other
algorithms on these labelled instances, except in the easy region at the left
of the graph.
